### 2014-10-14 PrivacyProtection-2014-09-09.tex
added threat example diagrams for man-in-the-middle and intransparency
did some refactoring on the sensor privacy matrix section

@@

\subsubsection{Threats}
\input{./figures/LG-Threats}
\input{./figures/ThreatTable}

%\begin{itemize}
%
%\item
%  \textbf{Unauthorized access to privacy sensitive data}, caused by
%  \begin{itemize}
%  \item
%    \textbf{Excessive Data Mining} Linking sensor data provided by
%    citizens with additional sources can produce more privacy sensitive
%    data.
%  \item
%    \textbf{Corrupt Local Authorities} Local Authorities have certain data
%    access, they could hand over this access for monetary reasons.
%  \item
%    \textbf{Corrupt/Unhappy Staff} Staff members also have a certain data
%    access and they also could hand over this access for monetary reasons
%    or as a form of payback for unfair treatment.
%  \item
%    \textbf{Competent Attackers} Competent Attackers are always a threat
%    for IT-systems. Normaly they have monetary reasons to exploit a
%    system, but there is also a possibility for proof-of-concept like
%    attacks.
%  \end{itemize}
%\end{itemize}
%
%
\paragraph{Sensor Privacy Matrix (Figure \ref{figure:Live+Gov Sensor-Privacy Matrix})}

@@

\subparagraph{Privacy of The Person}

@@

\subparagraph{Privacy of Data and Image}

@@

\subparagraph{Privacy of Location and Space}

@@

\subparagraph{Privacy of Associtation}

@@

>>>>

% test citing
%\cite{CFried:Privacy}
%\cite{WarrenBrandeis:RightToPrivacy}
%\cite{sep-privacy}
%\cite{7ToP}
%\cite{Grimm:ItSecRefModel}
%\cite{ItSecGlossary}
%\cite{SociotechnicalArchitectureForOnlinePrivacy}
%\cite{EUDataProtectionDirective}
%\cite{EUConventionOnHumanRights}
%\cite{Bundesdatenschutzgesetz}
%\cite{Gutwirth:DefiningPrivacy}
%\cite{UKDataProtectionAct}

@@

\subsubsection{Threat Specification}

\textbf{Man In The Middle:}
Lorem ipsum dolor suit amet, ...

\textbf{Exploit:}
Lorem ipsum dolor suit amet, ...

\textbf{Corruption:}
Lorem ipsum dolor suit amet, ...

\textbf{Intrasparency:}
Lorem ipsum dolor suit amet, ...

\input{./figures/LG-Threats}
\input{./figures/Threat-Example-1}
\input{./figures/Threat-Example-2}
\input{./figures/ThreatTable}

\subsubsection{Threat Risk Evaluation}

% Todo: use sensor privacy matrix and implicit sensor privacy matrix for threat risk evaluation

\textbf{Sensor Privacy Matrix}

@@

\item
\textbf{Privacy of The Person}

@@

@@

@@

\item
\textbf{Privacy of Associtation}

@@

\subsubsection{Security Requirement Specification}
